Modeling potential JCPOA diversion scenarios using Cyclus

### 2018-01-27 paper.tex

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.7]{flow_case_2_no_recy.pdf}
  \caption{Illustration of the material flow between the different level of
      cascades without tail recycling, in this diagram, nu\_src correspond to an
      infinite source of natural uranium, cascade\_ $n$ and storage\_ $n$
      corresponds respectively to the cascades, and the storage getting the
  products of the cascades at the level $n$.}\label{fig:flow}
\end{figure}

@@

The case 1 is designed to configure identical 30 cascades in the scenario (the maximum
allowable under the JCPOA agreement). The basic
properties are: less than 169 centrifuges per cascade, F/P/T assays of
0.0071/0.035/0.003. The corresponding cascade design includes 167 centrifuges, with
respective F/P/T assays of 0.0071/0.0412842/0.00290548.

>>>>

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.68]{flow_case_2_no_recy.pdf}
  \caption{Illustration of the material flow between the different level of
      cascades without tail recycling, in this diagram, nu\_src corresponds to
      an infinite source of natural uranium, cascade\_ $\{n\}$ and storage\_
      $\{n\}$ to the cascade and the storage getting the products of the
      cascades at the level $\{n\}$.}\label{fig:flow}
\end{figure}

@@

The case 1 is designed to configure identical 30 cascades in the scenario (the maximum
allowable under the JCPOA agreement). The basic
properties are: less than 169 centrifuges per cascade, F/P/T assays of
0.0071/0.035/0.003. The corresponding cascade design includes 167 centrifuges, with
respective F/P/T assays of 0.0071/0.0413/0.002.
